Efficient Community Formation \\ for Web Services

### 2013-12-29 papers/coalition-journal-R1/coalition_journal_r1.tex
changes

>>>>

\textbf{Web Service Community.}
Community in general refers to the condition of sharing or having certain
attitudes and interests in common. Communities of web services 
\cite{DBLP:journals/internet/BenatallahSD03,
Zeng:2003:QDW:775152.775211}, the authors introduce community of
web services as collection of cooperative web services with common
functionalitiers but different QoS metrics. Therefore
$communities$ are differentiated from $composition$ types of web
service cooperation in which web services with different
functionalities work together to generate a new service with
composite functionality.

Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities. This
architecture has been further developed in
\cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10,
conf/aina/LimTM11, CSTintercommunity}. Two types of roles have
been distinguished for community members: masters and slaves.
Master web services lead communities and are responsible for
membership management. They can invite and convince slave web
services to join the community, and attract new slave web services
to their communities by awarding them better payoff. Moreover,
they can eject some slave members from the community to improve
its overall reputation if these members are misbehaving or cannot
provide the promised QoS \cite{DBLP:journals/ijebr/MaamarSTBB09}.
